Lyman-$\alpha$ photons through rotating outflows

### 2018-03-28 paper/paper.tex
paper descrip

where each $m_i$ is the i-th moment about the mean. The STD has velocity units and 
quantifies the dispersion of the line's velocity: the larger it is, the wider the line. 
The SKW is adimensional and quantifies the peaks' asymmetry: if it is $>0$ the left peak is 
taller and if it is $<0$ the right peak is taller. The BI has velocity$^{-1}$ units and
quantifies if the line has 1 or 2 peaks: it is always $\geq 1$ and the closer it is to 1 the more
bimodal is the line (i.e. has 2 peaks).

>>>>

where each $m_i$ is the i-th moment about the mean. The STD has velocity units and 
quantifies the dispersion of the line's velocity: the larger it is, the wider the line. 
The SKW has velocity$^{-1/2}$ units and quantifies the peaks' asymmetry: if it is $>0$ the left peak is 
taller and if it is $<0$ the right peak is taller. The BI has velocity$^{-1}$ units and
quantifies if the line has 1 or 2 peaks.
